Many Analystis Project

### 2022-01-02 analysis.Rmd
small change
Update analysis.Rmd
removed whitespace
Update analysis.Rmd

```{r global_options, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(#
  fig.path="Figs/", 
  message=FALSE, 
  warning=FALSE,
  collapse =TRUE,
  echo=TRUE, 
  #results="hide", 
  fig.width= 10,
  fig.height=10,
  tidy = "styler")
```

```{r runanalysis, echo=FALSE, include = FALSE}
source("libs.R") # libraries 
source("funs.R") # custom functions

# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
#library("papaja")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

## correlation

@@

Graph for confounding

```{r}
library(patchwork)
m0 <- lmer(
    anx ~
    bg_s +
  #  ch_s +
    age_s  +
    male +
    ( bg_s | country), 
  data = d1)

sjPlot::tab_model(m0)

m0 <- brm(
  anx ~
    bg_s +
    #ch_s +
    age_s  +
    male +
    (1 + bg_s | country),
  data = d1,
  family = cumulative(link = "logit"),
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m2o_real")
)

@@

###  Model
```{r}
m1 <- brm(
  anx ~
    bg_s +
    ch_s +
    age_s  +
    male +
    (1 + bg_s | country),
  data = d1,
  family = cumulative(link = "logit"),
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m2o_real")
)

@@

## Simulation tables

>>>>

```{r global_options, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(#
  fig.path="Figs/", 
  message=FALSE, 
  warning=FALSE,
  collapse =TRUE,
  echo=TRUE, 
  #results="hide", 
  fig.width= 16,
  fig.height= 9)
```

```{r runanalysis, echo=FALSE, include = FALSE}
#source("libs.R") # libraries 
# source("funs.R") # custom functions

# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
#library("papaja")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

### correlation

@@

### Check LMER Results

```{r}
library(patchwork)
mlmerCH <- lmer(
    anx ~
    #bg_s +
    ch_s +
    age_s  +
    male +
    ( 1 + ch_s | country), 
  data = d1)

sjPlot::tab_model(mlmerCH)

mlmerBG <- lmer(
    anx ~
    bg_s +
    ch_s +
    age_s  +
    male +
    ( 1 + bg_s | country), 
  data = d1)

sjPlot::tab_model(mlmerBG)
```

## General Estimating Equations

### IPW Anxiety ~ Belief

```{r}
library("ipw")

d1ipwB <- ipw::ipwpoint(
  exposure = bg_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~  ch_s + age_s  + male + country,
  data = as.data.frame(d1)
)

summary(d1ipwB$ipw.weights)
sum(d1ipwB$ipw.weights > 10)

d1pB <- d1 %>% 
  mutate(ipw = d1ipwB$ipw.weights) %>%
  filter(ipw < 10)
```

Model:

```{r}
mgeeB  <- geeglm(
  anx ~
    bg_s,# + # already weighted
   # ch_s +
   # age_s  +
   # male,
  data = d1pB,
  id = country,
  weights = ipw
)

parameters::model_parameters(mgeeB) %>%
  print_html()

library(ggeffects)
p0BG <- plot(ggeffects::ggemmeans(mgeeB, terms = "bg_s [all]"), add.data = TRUE, dot.alpha = 0.1)    # 
p0BG 
```

### IPW Anxiety ~ Church

First we create Inverse Probability Weights

```{r}
library("ipw")

d1ipw <- ipw::ipwpoint(
  exposure = ch_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~  age_s  + male + country,
  data = as.data.frame(d1)
)

summary(d1ipw$ipw.weights)
sum(d1ipw$ipw.weights > 10)

d1p <- d1 %>% 
  mutate(ipw = d1ipw$ipw.weights)
```

Model

```{r}
mgeeCH <- geeglm(
  anx ~
    ch_s,# + # already weighted
    #age_s  +
  #  male,
  data = d1p,
  id = country,
  weights = ipw
)

parameters::model_parameters(mgeeCH) %>%
  print_html()

library(ggeffects)
pmgeeCH <- plot(ggeffects::ggemmeans(mgeeCH, terms = "ch_s [all]"), add.data = TRUE, dot.alpha = 0.1)    # 
pmgeeCH
```

Model with with trimmed IPW (as recommended to avoid leverage from rare cases). Note, the result here is the same.

```{r, eval = FALSE}

# trim IPW to less than 10 
d1pf <- d1 %>% 
  mutate(ipw = d1ipw$ipw.weights) %>%
  filter(ipw < 10)

m0f <- geeglm(
  anx ~
    ch_s,# +
    #age_s  +
  #  male,
  data = d1pf,
  id = country,
  weights = ipw
)

parameters::model_parameters(m0f) %>%
  print_html()

library(ggeffects)
p0f <- plot(ggeffects::ggemmeans(m0f, terms = "ch_s [all]"), add.data = TRUE, dot.alpha = 0.1)    # 
p0f
```

@@

```{r}
m1 <- brm( 
  anx ~
    bg_s +
    ch_s +
    age_s  +
    male +
    (1 + bg_s | country),
  data = d1,
  family = cumulative(link = "logit"),
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m2o_real")
)

@@

˝## Simulation tables
